---
title: "ACRV"
output: html_document
date: "2024-03-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


First, let's pull some basics - what model was preferred by what dataset?
```{r}

alpha_values <-c(0)
alpha_indicators <-c(0)
names <-c(0)

for (file in list.files(path=".", pattern=".log")){
  data <- read_delim(file)
  names <- c(names, file)
  median = median(data$alpha)
  med_ind = median(data$alpha_indicator)
  alpha_values <- c(alpha_values, median)
  alpha_indicator <- c(alpha_indicator, med_ind)
}
```


Next, let's grab the differences between the largest and smallest Gamma categories.

```{r}
diffs <-c(0)

for (file in list.files(path=".", pattern=".log")){
  data <- read_delim(file)
  names <- c(names, file)
  median1 = median(data$`site_rates[1]`)
  median2 = median(data$`site_rates[2]`)
  median3 = median(data$`site_rates[3]`)
  median4 = median(data$`site_rates[4]`)
  median_vec <- c(median1, median2, median3, median4)
  min_med <- min(median_vec)
  max_med <- max(median_vec)
  diffs <- c(diffs, max_med - min_med)
}
```

Wrap it all up in a dataframe:

```{r}

alpha_indicators <- alpha_indicators[2:572]
names <- names[2:572]
alpha_values <- alpha_values[2:572]
diff_values <- diffs[2:572]

dataframe <- data.frame(names, alpha_indicators, alpha_values, diff_values)

```

And plot: 

First, model preferences. 
```{r}

dataframe %>% 
  count(alpha_indicators == 1)
# Quick count - 405 of 577 datasets favor Rate Het
ggplot(dataframe, aes(x = alpha_indicators)) + geom_density()

```

Extremes. Either the data strongly favor rate het or they do not. 


```{r}
dataframe %>% 
  count(alpha_values > 100)
# For the datasets, about half have a distribution that implies a heavily concentrated set of rates (ie, little rate variation, but not none). We probably want a figure in here of how different gamma dists look

ggplot(dataframe, aes(x = alpha_values)) + geom_density()


```
Favortism for extremes: on the upper end, no rate het. On the lower end, strong rate het.

Now for the differences in the rate categories between the smallest and largest rates. 
```{r}
ggplot(dataframe, aes(x = diffs)) + geom_density()

```
Now let's strip this to only data for which there is no model preference for rate het:

```{r}
filtered <- dataframe %>% 
  filter(alpha_indicators != 1) 
ggplot(filtered, aes(x = diff_values)) + geom_density()


```
Makes sense - if the MCMC doesn't prefer rate het, our rate categories are all the same. Good. Now let's strip this to only data for which there is  model preference for rate het:

```{r}
filtered <- dataframe %>% 
  filter(alpha_indicators == 1) 
ggplot(filtered, aes(x= diff_values)) + geom_histogram()
```

This is interesting because there is still a good amount of datasets for which there is a preference for rate het, but then the categories are the same. Hm. 

You can try some different values in here. But basically, for about a third of data sets with rate het, the rate het is quite small.

```{r}
dataframe %>% 
  filter(alpha_indicators == 1) %>% 
  count(diff_values <= .005)

mean(dataframe$diff_values, na.rm = TRUE)
median(dataframe$diff_values, na.rm = TRUE)

```

